%\documentclass[11pt,a4paper]{article}
\documentclass[11pt
  , a4paper
  , article
  , oneside
%  , twoside
%  , draft
]{memoir}

\usepackage{control}
\usepackage[numbers]{natbib}


\begin{document}

\newcommand{\technumber}{
  RAON Control-Document Series\\
  Revision : v0.1,   Release : 2015. 05. 29}
\title{\textbf{Alive}}

\author{Seung Hee Nam\thanks{namsh@ibs.re.kr} \\
  Control Team \\
  Rare Isotope Science Project\\
  Institute for Basic Science\\
  Daejeon, South Korea
}

\date{\today}

\renewcommand{\maketitlehooka}{\begin{flushright}\textsf{\technumber}\end{flushright}}
%\renewcommand{\maketitlehookb}{\centering\textsf{\subtitle}}
%\renewcommand{\maketitlehookc}{C}
%\renewcommand{\maketitlehookd}{D}

\maketitle

\begin{abstract}
Alive record is device support for simple network ping include variable information. This paper handling alive and using alive for monitoring dynamic IOC.
\end{abstract}



\chapter{What is alive?}
Alive record was made by Dohn Arms to monitoring dynamic IOC. Alive module is device support for a simple network ping, and that using custom heartbeat protocol and external heartbeat-watching program. Alive send UDP packet every 15 second to a specified address and port. This UDP packet contains  heartbeat counter, current time and so on. The record also opens a TCP port that allows receiving static information about the IOC. On the remote server, the UDP packets are collected by a daemon into a database to monitor the IOCs. The IP address is gotten from the packet itself.
\section{The structure of alive-1-0}
  \begin{verbatim}
   |--   aliveApp
   |   |--   Db
   |   |   |--   alive.db
   |   |   `--   Makefile
   |   |--   Makefile
   |   |--   op
   |   |   |--   adl
   |   |   |   `--   aliveRecord.adl
   |   |   |--   opi
   |   |   |   `--   aliveRecord.opi
   |   |   `--   ui
   |   |       `--   aliveRecord.ui
   |   `--   src
   |       |--   aliveExMain.cpp
   |       |--   aliveRecord.c
   |       |--   aliveRecord.dbd
   |       |--   aliveSupport.dbd
   |       `--   Makefile
   |--   configure
   |   |--   CONFIG
   |   |--   CONFIG_SITE
   |   |--   Makefile
   |   |--   RELEASE
   |   |--   RULES
   |   |--   RULES_DIRS
   |   |--   RULES.ioc
   |   `--   RULES_TOP
   |--   documentation
   |   |--   aliveDoc.html
   |   |--   aliveRecord.html
   |   |--   aliveRecord.png
   |   |--   aliveReleaseNotes.html
   |   `--   aliveServer.html
   |--   iocBoot
   |   |--   iocaliveEx
   |   |   |--   Makefile
   |   |   |--   README
   |   |   `--   st.cmd
   |   `-- [namsh     121]  Makefile
   |--   Makefile
   `--   start_epics

   \end{verbatim}
   \section{Important alive module file}
   
      \begin{itemize}
      	\item EPICS Database\\
      	alive.db 
      	\item MEDM display file\\
      	aliveRecord.adl
      	\item Record\\
      	aliveRecord.html,
      	aliveServer.html
      	   \end{itemize}
      	   http://www.aps.anl.gov/bcda/synApps/alive/aliveDoc.html
      	
   \clearpage
   



\end{document}
